---
title: "Mental_Health_Cal_Productivity_Lost"
author: "Niket Choudhary"
date: "August 5, 2018"
output: rmarkdown::github_document
---

```{r}
mhealth_2 <- read.csv(file.choose(), header = TRUE, na.strings = c("NA", "", " ", "."))
```

```{r}
summary(mhealth_2)
```

***

Let's convert factors to 0 and 1 and 2 depending on their effects


```{r}
# self_employed Are you self-employed? Yes : 0, No : 1

levels(mhealth_2$self_employed)[levels(mhealth_2$self_employed) == "Yes"] <- '0'
levels(mhealth_2$self_employed)[levels(mhealth_2$self_employed) == "No"] <- '1'


# family_history Do you have a family history of mental illness? Yes : 1, No : 0

levels(mhealth_2$family_history)[levels(mhealth_2$family_history) == "No"] <- '0'
levels(mhealth_2$family_history)[levels(mhealth_2$family_history) == "Yes"] <- '1'

# treatment Have you sought treatment for a mental health condition? Yes : 0, No : 1

levels(mhealth_2$treatment)[levels(mhealth_2$treatment) == "Yes"] <- '0'
levels(mhealth_2$treatment)[levels(mhealth_2$treatment) == "No"] <- '1'


# work_interfere

mhealth_2$work_interfere <- as.factor(mhealth_2$work_interfere) 


# no_employeesHow many employees does your company or organization have? Leave this

# remote_work Do you work remotely (outside of an office) at least 50% of the time? Yes : 0, No : 1

levels(mhealth_2$remote_work)[levels(mhealth_2$remote_work) == "Yes"] <- '0'
levels(mhealth_2$remote_work)[levels(mhealth_2$remote_work) == "No"] <- '1'

# tech_company Is your employer primarily a tech company/organization? Leave this

# benefitsDoes your employer provide mental health benefits? Yes : 0, No : 2, Don't know : 1

levels(mhealth_2$benefits)[levels(mhealth_2$benefits) == "Yes"] <- '0'
levels(mhealth_2$benefits)[levels(mhealth_2$benefits) == "No"] <- '2'
levels(mhealth_2$benefits)[levels(mhealth_2$benefits) == "Don't know"] <- '1'

# care_options Do you know the options for mental health care your employer provides? No : 2, Not sure : 1, Yes : 0

levels(mhealth_2$care_options)[levels(mhealth_2$care_options) == "Yes"] <- '0'
levels(mhealth_2$care_options)[levels(mhealth_2$care_options) == "No"] <- '2'
levels(mhealth_2$care_options)[levels(mhealth_2$care_options) == "Not sure"] <- '1'

# wellness_program Has your employer ever discussed mental health as part of an employee wellness program? Yes : 0, No : 2, Don't know : 1

levels(mhealth_2$wellness_program)[levels(mhealth_2$wellness_program) == "Yes"] <- '0'
levels(mhealth_2$wellness_program)[levels(mhealth_2$wellness_program) == "No"] <- '2'
levels(mhealth_2$wellness_program)[levels(mhealth_2$wellness_program) == "Don't know"] <- '1'

# seek_help Does your employer provide resources to learn more about mental health issues and how to seek help? Yes : 0, No : 2, Don't know : 1

levels(mhealth_2$seek_help)[levels(mhealth_2$seek_help) == "Yes"] <- '0'
levels(mhealth_2$seek_help)[levels(mhealth_2$seek_help) == "No"] <- '2'
levels(mhealth_2$seek_help)[levels(mhealth_2$seek_help) == "Don't know"] <- '1'


# anonymity Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources? Yes : 0, No : 2, Don't know : 1

levels(mhealth_2$anonymity)[levels(mhealth_2$anonymity) == "Yes"] <- '0'
levels(mhealth_2$anonymity)[levels(mhealth_2$anonymity) == "No"] <- '2'
levels(mhealth_2$anonymity)[levels(mhealth_2$anonymity) == "Don't know"] <- '1'

# leave How easy is it for you to take medical leave for a mental health condition? Don't know : 1, Somewhat difficult : 3, Somewhat easy : 2, Very difficult : 4, Very easy : 0

levels(mhealth_2$leave)[levels(mhealth_2$leave) == "Very easy"] <- '0'
levels(mhealth_2$leave)[levels(mhealth_2$leave) == "Don't know"] <- '1'
levels(mhealth_2$leave)[levels(mhealth_2$leave) == "Somewhat easy"] <- '2'
levels(mhealth_2$leave)[levels(mhealth_2$leave) == "Somewhat difficult"] <- '3'
levels(mhealth_2$leave)[levels(mhealth_2$leave) == "Very difficult"] <- '4'

# mental_health_consequence Do you think that discussing a mental health issue with your employer would have negative consequences? No : 0, Maybe : 1, Yes : 2

levels(mhealth_2$mental_health_consequence)[levels(mhealth_2$mental_health_consequence) == "Yes"] <- '2'
levels(mhealth_2$mental_health_consequence)[levels(mhealth_2$mental_health_consequence) == "No"] <- '0'
levels(mhealth_2$mental_health_consequence)[levels(mhealth_2$mental_health_consequence) == "Maybe"] <- '1'

# phys_health_consequence Do you think that discussing a physical health issue with your employer would have negative consequences? No : 0, Maybe : 1, Yes : 2

levels(mhealth_2$phys_health_consequence)[levels(mhealth_2$phys_health_consequence) == "Yes"] <- '2'
levels(mhealth_2$phys_health_consequence)[levels(mhealth_2$phys_health_consequence) == "No"] <- '0'
levels(mhealth_2$phys_health_consequence)[levels(mhealth_2$phys_health_consequence) == "Maybe"] <- '1'

# coworkers Would you be willing to discuss a mental health issue with your coworkers? No : 2, Some of them : 1, Yes : 0

levels(mhealth_2$coworkers)[levels(mhealth_2$coworkers) == "Yes"] <- '0'
levels(mhealth_2$coworkers)[levels(mhealth_2$coworkers) == "No"] <- '2'
levels(mhealth_2$coworkers)[levels(mhealth_2$coworkers) == "Some of them"] <- '1'

# supervisor Would you be willing to discuss a mental health issue with your direct supervisor(s)? No : 2, Some of them : 1, Yes : 0

levels(mhealth_2$supervisor)[levels(mhealth_2$supervisor) == "Yes"] <- '0'
levels(mhealth_2$supervisor)[levels(mhealth_2$supervisor) == "No"] <- '2'
levels(mhealth_2$supervisor)[levels(mhealth_2$supervisor) == "Some of them"] <- '1'

# mental_health_interviewWould you bring up a mental health issue with a potential employer in an interview? Leave this
# phys_health_interviewWould you bring up a physical health issue with a potential employer in an interview? Leave this

# mental_vs_physical Do you feel that your employer takes mental health as seriously as physical health? Yes : 0, No : 2, Don't know : 1

levels(mhealth_2$mental_vs_physical)[levels(mhealth_2$mental_vs_physical) == "Yes"] <- '0'
levels(mhealth_2$mental_vs_physical)[levels(mhealth_2$mental_vs_physical) == "No"] <- '2'
levels(mhealth_2$mental_vs_physical)[levels(mhealth_2$mental_vs_physical) == "Don't know"] <- '1'


# obs_consequence Have you heard of or observed negative consequences for coworkers with mental health conditions in your workplace? Yes : 1, No : 0

levels(mhealth_2$obs_consequence)[levels(mhealth_2$obs_consequence) == "Yes"] <- '1'
levels(mhealth_2$obs_consequence)[levels(mhealth_2$obs_consequence) == "No"] <- '0'
```

***

```{r}
str(mhealth_2)
```

Drop unnecessary columns
```{r}
mhealth_2$Country <- NULL
mhealth_2$no_employees <- NULL
mhealth_2$tech_company <- NULL
mhealth_2$mental_health_interview <- NULL
mhealth_2$phys_health_interview <- NULL
```

Create new column named Productivity Loss with the sum of above values
```{r}
mhealth_2$productivity_loss <- (as.numeric(as.character(mhealth_2$self_employed)) + as.numeric(as.character(mhealth_2$family_history)) + as.numeric(as.character(mhealth_2$treatment)) + as.numeric(as.character(mhealth_2$work_interfere)) + as.numeric(as.character(mhealth_2$remote_work)) + as.numeric(as.character(mhealth_2$benefits)) + as.numeric(as.character(mhealth_2$care_options)) + as.numeric(as.character(mhealth_2$wellness_program)) + as.numeric(as.character(mhealth_2$seek_help)) + as.numeric(as.character(mhealth_2$anonymity)) + as.numeric(as.character(mhealth_2$leave)) + as.numeric(as.character(mhealth_2$mental_health_consequence)) + as.numeric(as.character(mhealth_2$phys_health_consequence)) + as.numeric(as.character(mhealth_2$coworkers)) + as.numeric(as.character(mhealth_2$supervisor)) + as.numeric(as.character(mhealth_2$mental_vs_physical)) + as.numeric(as.character(mhealth_2$obs_consequence)))
```

```{r}
summary(mhealth_2$productivity_loss)
```

So, now our scale for Productivity Lost ranges from 2 to 30


Also, bin our loss of productivity into 3 age groups: 
- Younger than 25
- 25-50
- 50+ 
```{r}
mhealth_2$Age1 <- '50+'
mhealth_2$Age1[mhealth_2$Age < 50 & mhealth_2$Age >= 25 ] <- '25-50'
mhealth_2$Age1[mhealth_2$Age < 25] <- 'Younger than 25'
```

```{r}
summary(as.factor(mhealth_2$Age1))
```


```{r}
library(ggplot2)
# Plot predictions vs test data
ggplot(mhealth_2,aes(Age, (productivity_loss))) +
      geom_point(color = "darkred", alpha = 0.5) + 
      geom_smooth(method = lm)+ ggtitle('Linear Regression ') +
      ggtitle("Linear Regression: Age vs productivity_loss") +
      xlab("Age") +
      ylab("productivity_loss") +
      theme(plot.title = element_text(color="darkgreen",size=18,hjust = 0.5),
                     axis.text.y = element_text(size=12),
          
            axis.text.x = element_text(size=12,hjust=.5),
                      axis.title.x = element_text(size=14),
            axis.title.y = element_text(size=14))
   
```


```{r}
ggplot(mhealth_2, aes(x = Age1, y = productivity_loss)) +
        geom_boxplot()
```
Highest Productivity Loss is seen in the younger population below 25 and 25 to 50. Loss decreases slightly at 50+

```{r}
ggplot(mhealth_2, aes(productivity_loss)) +
  geom_density(aes(fill = Age1), alpha = 0.4)
```
Higher population is suffering from loss of about 12 to 18, with a fewer population showing higher than 25 value. Also most are 50+ with productivity loss of 30.

```{r}
length(mhealth_2$productivity_loss)

mean(mhealth_2$productivity_loss)

sd(mhealth_2$productivity_loss)
```

calculate an error for the mean:
```{r}
error <- qt(0.975,df = length(mhealth_2$productivity_loss) - 1) * sd(mhealth_2$productivity_loss) / sqrt(length(mhealth_2$productivity_loss))
error
```

we will find confidence interval by adding and subtracting the error from the mean
```{r}
left <- mean(mhealth_2$productivity_loss) - error
right <- mean(mhealth_2$productivity_loss) + error
left
right
```
There is a 95% probability that the true mean is between 14.96779 and 15.57858 assuming that the original random variable is normally distributed, and the samples are independent.


